---
title: "Presentations by Year"
author: "Matthew Renze"
date: "May 21, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

The following is data visualization of the number of public presentations that I have given (or am scheduled to give) at software and technology conferences each year as of May 21, 2017.

## Data Visualization

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load packages
library(plotly)
library(lubridate)
library(dplyr)

# Set working directory
setwd("C:/Work/School/Products/Projects/Project 3")

# Load presentation data
presentations <- read.csv("Presentations.csv")

# Convert date 
presentations$Date <- as.Date(
  x = presentations$Date,
  format = "%m/%d/%Y")

# Transform data
history <- presentations %>%
  select(Date) %>%
  group_by(Year = year(Date)) %>%
  summarize(Count = n()) %>%
  arrange(Year) %>%
  as.data.frame()

# Display bar chart
plot_ly(
  data = history,
  x = ~Year,
  y = ~Count,
  mode = "lines")%>%
  layout(
    title = "Count of Presentations by Year")
```

## Code

To create this data visualization, I used the following code.

```{r, echo=TRUE, results='hide', message=FALSE, warning=FALSE}
# Load packages
library(plotly)
library(lubridate)
library(dplyr)

# Set working directory
setwd("C:/Work/School/Products/Projects/Project 3")

# Load presentation data
presentations <- read.csv("Presentations.csv")

# Convert date 
presentations$Date <- as.Date(
  x = presentations$Date,
  format = "%m/%d/%Y")

# Transform data
history <- presentations %>%
  select(Date) %>%
  group_by(Year = year(Date)) %>%
  summarize(Count = n()) %>%
  arrange(Year) %>%
  as.data.frame()

# Display bar chart
plot_ly(
  data = history,
  x = ~Year,
  y = ~Count,
  mode = "lines")%>%
  layout(
    title = "Count of Presentations by Year")
```

## Conclusion

Thank you for taking a look at my data visualization.

For more information, please visit my website at: <http://www.matthewrenze.com>



